---
title: 'Peer-graded Assignment: Statistical Inference Course Project'
author: "Frank Hettmer"
date: "24 September 2017"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}

```


## R Markdown

Based on the given information lambda = 0.2, n = 40 an Simulations >= 1000

```{r}

lambda<-0.2
n<-40
simulations=1000
```

Generate simulation data and fill data in a matrix structure

```{r}

simulationdata<-rexp(n*simulations, lambda)
simulationmatrix =  matrix(simulationdata, nrow = 1000, ncol = 4)
```
Theoretical mean of exponential distribution is 1/lambda, i.e. 1/0.2 --> 5
Sample mean overall is mean by all drawings and samplemean by simulation is mean by simulation

```{r}

theomean<-1/lambda
samplemeanover<-mean(simulationdata)
samplemeanbysimulation<- apply(simulationmatrix,1,mean)
```

Theoretical Variance of exponential distribution is (1/lambda)^2, i.e. (1/0.2)^2 and sample varianz overall is mean by all drawings and sample variance by simulation by simulation

```{r}

theosd<-(1/lambda)
theovar<-(1/lambda)^2
samplevarover<-var(simulationdata)
samplevarbysimulation<- apply(simulationmatrix,1,var)
```

The results as overview:
Mean: theoretical   5 sample        4.9900

Standard Deviation: theoretical   5 sample        5.0049

Variance: theoretical   25 sample        25.0491

The histogramm shows that the distribution is approximately normal

```{r}
library(ggplot2)
hist(samplemeanbysimulation, col="darkblue", main="Theoretical vs actual mean for rexp()", breaks=20)
abline(v=mean(samplemeanbysimulation), lwd="4", col="red")
text(3.6, 90, paste("Actual mean = ", round(mean(samplemeanbysimulation),2), "\n Theoretical mean = 5" ), col="red")
```

